---
output: github_document
---

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# keyring

<!-- badges: start -->

[![R-CMD-check](https://github.com/r-lib/keyring/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/keyring/actions/workflows/R-CMD-check.yaml) [![](https://www.r-pkg.org/badges/version/keyring)](https://www.r-pkg.org/pkg/keyring) [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/keyring)](https://www.r-pkg.org/pkg/keyring) [![Codecov test coverage](https://codecov.io/gh/r-lib/keyring/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-lib/keyring?branch=main)

<!-- badges: end -->

keyring provides a way to securely manage secrets using your operating system's credential store.
Once a secret is defined, it persists in the keyring across multiple R sessions.
keyring is an alternative to using env vars that's a bit more secure because your secret is never stored in plain text, meaning that you can (e.g.) never accidentally upload it to GitHub.

keyring currently supports:

-   The macOS Keychain (`backend_macos`).
-   The Windows Credential Store (`backend_wincred`).
-   The Linux Secret Service API (`backend_secret_service`).

It also provides two backends that are available on all platforms:

-   Encrypted files (`backend_file`)
-   Environment variables (`backend_env`).

## Installation

Install the package from CRAN:

```{r eval = FALSE}
# install.packages("pak")
pak::pak("keyring")
```

We recommend using pak to install keyring as it will ensure that all Linux system requirements (e.g. `libsecret-devel`, `openssl-devel`) are automatically installed.

## Usage

The simplest usage only requires `key_set()` and `key_get()`:

```{r}
#| eval: false

# Interactively save a secret. This avoids typing the value of the secret
# into the console as this will be recorded in your `.Rhistory`
key_set("secret-name")

# Later retrieve that secret
key_get("secret-name")
```

Each secret is associated with a keyring.
By default, keyring will use the OS keyring (see `default_backend()` for details), which is automatically unlocked you log in.
That means while the secret is stored securely, it can be accessed by other processes.

If you want greater security you can create a custom keyring that you manually lock and unlock.
That will require you to enter your system password every time you want to access your secret.

```{r}
#| eval: FALSE
keyring_create("mypackage")
key_set("MY_SECRET", keyring = "mypackage")
key_get("MY_SECRET", keyring = "mypackage")
```

Note that accessing the key unlocks the keyring, so if you're being really careful, make sure to lock it again afterwards.

```{r}
#| eval: false
keyring_lock("httr")
```

## Development documentation

Please see our [writeup of some `keyring` internals](https://github.com/r-lib/keyring/blob/main/inst/development-notes.md), and as always, use the source code.
